Evolution of Narrow-Band Spectra in Deep-Water Constant Vorticity Flows

### 2019-09-03 Writeup/random_vorticity.tex
Moving on

To generate simulations, we start both the NLSE and VDE from the same collection of $2L$ periodic-initial conditions
\[
\eta_{1}(\xi,0) = \epsilon_{rms}\sqrt{\frac{\delta \tilde{k}}{\sigma\sqrt{\pi}}} \sum_{k=-K+1}^{K}e^{-\tilde{k}^{2}/2\sigma^{2}}e^{i\theta_{k}}e^{i\tilde{k}\xi}, ~ \tilde{k} = \frac{\pi k}{L},
\]
where $\delta \tilde{k}=\pi/L$ and the phases $\theta_{k}$ are randomly chosen uniformly between $0$ and $2\pi$.  We can then readily show that, for $L\gg 1$, 
\[
\epsilon_{rms} \approx \overline{\left|\eta_{1}\right|^{2}}^{1/2},
\]
where $\overline{()}$ denotes the ensemble average.  In our coordinates then, the work in \cite{alber} and later confirmed in \cite{dysthe2} shows that for the NLSE the MI is suppressed for spectral widths $\sigma$ such that 
\[
\sigma \geq \sigma_{c}, ~ \sigma_{c} = \epsilon_{rms}\sqrt{\frac{2\alpha_{nl}}{\alpha_{d}}}
\]
This work has helped motivate defining this parameter as the Benjamin--Feir Index (BFI), which has been shown to be a critical parameter to understanding the statstical properties of nonlinear free-surface flows; see \cite{onorato, thomas2012nonlinear}.
\section*{Results}
To understand the relationship between the vorticity $\omega$ and the initial spectral width $\sigma$ of our initial conditions, we generate ensembles of initial conditions and then run these different initial conditions up to $\tau=1$, which corresponds to $t_{f} = 1/\epsilon^{2}$ in the original fast variables.  The domain is $[-50\pi,50\pi]$.  The number of modes is $K = 256$.  The surface tension is $\tilde{\sigma} = 10^{-5}$. We then plot the averaged spectral density $S(k,t_{f};\sigma)$ where 
\[
S\left(k,t_{f};\sigma\right) = \overline{\left( \left|\frac{1}{\epsilon}\hat{\eta}_{1}\left(\frac{k-k_{0}}{\epsilon},1;\sigma \right)\right|^{2}\right)}.
\]
which corresponds to the autocorrelation of the surface profile with respect to space.  Note we have emphasized the dependence on the initial spectral width $\sigma$ for the sake of clarity.  Following the approach in \cite{dysthe2,dysthe3}, by comparing the initial spectral density to that at later times, we can see directly whether MI manifests as significant distortions of the statistics, or if through supression the distributions remain relatively close to one another.

>>>>

To generate simulations, we start both the NLSE and VDE from the same collection of $2L$ periodic-initial conditions
\[
\eta_{1}(\xi,0) = \epsilon_{rms}\sqrt{\frac{\delta \tilde{k}}{\sigma\sqrt{\pi}}} \sum_{k=-K+1}^{K}e^{-\tilde{k}^{2}/2\sigma^{2}}e^{i\theta_{k}}e^{i\tilde{k}\xi}, ~ \tilde{k} = \frac{\pi k}{L},
\]
where $\delta \tilde{k}=\pi/L$ and the phases $\theta_{k}$ are randomly chosen uniformly between $0$ and $2\pi$.  We can then readily show that, for $L\gg 1$, 
\[
\epsilon_{rms} \approx \overline{\left|\eta_{1}\right|^{2}}^{1/2},
\]
where $\overline{()}$ denotes the ensemble average.  In our coordinates then, the work in \cite{alber} and later confirmed in \cite{dysthe2} shows that for the NLSE the MI is suppressed for spectral widths $\sigma$ such that 
\[
\sigma \geq \sigma_{c}, ~ \sigma_{c} = \epsilon_{rms}\sqrt{\frac{2\alpha_{nl}}{\alpha_{d}}}
\]
This work has helped motivate defining this parameter as the Benjamin--Feir Index (BFI), which has been shown to be a critical parameter to understanding the statstical properties of nonlinear free-surface flows; see \cite{onorato, thomas2012nonlinear}.
\section*{Results}
To understand the relationship between the vorticity $\omega$ and the initial spectral width $\sigma$ of our initial conditions, we generate ensembles of initial conditions and then run these different initial conditions up to $\tau=2$ which corresponds to $t_{f} = 2/\epsilon^{2}$ in the original fast variables.  The domain is $[-50\pi,50\pi]$.  The number of modes is $K = 512$.  The surface tension is $\tilde{\sigma} = 10^{-5}$. We then plot the averaged spectral density $S(k,t_{f};\sigma)$ where 
\[
S\left(k,t_{f};\sigma\right) = \overline{\left( \left|\frac{1}{\epsilon}\hat{\eta}_{1}\left(\frac{k-k_{0}}{\epsilon},1;\sigma \right)\right|^{2}\right)}.
\]
which corresponds to the autocorrelation of the surface profile with respect to space.  Note we have emphasized the dependence on the initial spectral width $\sigma$ for the sake of clarity.  Following the approach in \cite{dysthe2,dysthe3}, by comparing the initial spectral density to that at later times, we can see directly whether MI manifests as significant distortions of the statistics, or if through supression the distributions remain relatively close to one another.
